\section{The Clock Synchronization Protocol with Public Setup}
\label{sec:protocol-details}

In this section we present the general approach and the various core building blocks of the new clock synchronization protocol---\timekeeper.
%
For a complete description, refer to~\cref{sec:complete-protocol-description}.
%
At a high level, \timekeeper is a Nakamoto-style PoW-based blockchain protocol together with time synchronization functionalities.
%
Readers can think of it as a Bitcoin protocol with the following modifications (See~\cref{fig:protocol-execution} for an illustration of the protocol execution).

\input{figures/protocol-execution}

\begin{cccItemize}[noitemsep]
    \item It replaces Bitcoin's original clock maintenance solution\footnote{In Bitcoin's original implementation, miners will adjust their time based on three different sources: (i) their local system clock; (ii) the median of clock values from peers; (iii) the human operator (if the first two disagrees).} with a new clock synchronization scheme, which requires parties to use 2-for-1 PoWs~\cite{EC:GarKiaLeo15} to mine and emit clock synchronization beacons and include them in an upcoming block.
    %
    Furthermore, protocol participants will periodically adjust their local clock values based on the beacons collected in the blockchain and their (local) receiving time.

    \item Events are triggered by counting the number of local rounds (which is different from the convention that events in PoW-based blockchains are triggered by the arrival of blocks).
    %
    In other words, the protocol has a clock synchronization \emph{interval} of length \syncLen and a target recalculation \emph{epoch} of length \diffLen that are defined in terms of the number of rounds; in addition, \diffLen is a multiple of \syncLen.
    %
    Both of these values are hardcoded in the protocol.
    %
    More precisely, parties will call the \textsf{SyncProcedure} sub-protocol (see~\cref{protocol:sync-proc}) when their local clock enters round \protocolTime{\interval}{\interval \cdot \syncLen} (this represents the last round in interval \interval; see below for details on the round structure); and for target in the next epoch they will call \textsf{UpdateMiningTarget} (\cref{protocol:update-mining-target}) when their local clock enters \protocolTime{\interval}{\interval \cdot \syncLen}, where $(\interval \mod (\diffLen / \syncLen)) = 0$ (i.e., at the boundary of every $(\diffLen / \syncLen)$ synchronization intervals).
\end{cccItemize}

Next, we present the basic components that are employed in \timekeeper.

\input{content/protocol-details/protocol-timestamps}
\input{content/protocol-details/sync-beacons}
\input{content/protocol-details/sync-intervals-procedure}
\input{content/protocol-details/target-recalculation}
\input{content/protocol-details/newly-joint-parties}
